Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/appendix.tex
address reviewer concerns about presentation of efficiency
move TraversableOnce code to appendix

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}.

@@

    Furthermore, $\lcc_\rcc$ is a finite set. 
    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types. There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
    \[
      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
    \]
    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
    \item All operations can be computed in $O(\rcc\times T)$ time. Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
    \item The space bound is $O(\rcc\times T)$.\qedhere
  \end{enumerate}
\end{proof}

>>>>

\section{TraversableOnce Trait from Scala Standard Library}

\begin{figure}
\inputMinted{scala}{TraversableOnce.scala}
\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
\label{fig:traversableonce}
\end{figure}

\section{Proofs}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}.

@@

    Furthermore, $\lcc_\rcc$ is a finite set. 
    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types. There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
    \[
      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
    \]
    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
    \item All operations can be computed in $O(\rcc\times T)$ time. %Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
    \item The space bound is $O(\rcc\times T)$.\qedhere
  \end{enumerate}
\end{proof}

### 2015-03-08 sas2015/content/example.tex
move TraversableOnce code to appendix

The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce}.

\begin{figure}
\inputMinted{scala}{TraversableOnce.scala}
\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
\label{fig:traversableonce}
\end{figure}

>>>>

The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce} in the appendix.
